Data Cleaning

### 2025-12-08 Data Cleaning.Rmd
Preliminary assessment for classification algorithm of dose change.

write_csv(class_df, "RWAR_dosing_lag_incdec.csv")

@@

>>>>

@@

```{r}
write_csv(class_df, "RWAR_dosing_lag_incdec.csv")
```

### Classification

df_lag_incdec <- read.csv("RWAR_dosing_lag_incdec.csv")

df_lag_incdec$FeCl_change <- as.factor(df_lag_incdec$FeCl_change)
df_lag_incdec$Polymer_change <- as.factor(df_lag_incdec$Polymer_change)

summary(df_lag_incdec)

df_lag_incdec <- df_lag_incdec |> 
  mutate(Timestamp = ymd(df_lag_incdec$Timestamp))

df_lag_incdec |>
  select(-c(Timestamp)) |>
  group_by(FeCl_change) |>
  summarise(mean_Temp = mean(mean_Temp),
            mean_pH = mean(mean_pH),
            mean_cond = mean(mean_Conductivity),
            mean_turbidity = mean(mean_Turbidity))

# counts for FeCl change
summary(df_lag_incdec$FeCl_change)
# counts for polymer change
summary(df_lag_incdec$Polymer_change)
